### 2019-05-08 doc/bilevel/CommonAbstract.tex
Fixing Anya's last edits
The main.tex file should not have been used here.  I moved the
edits to the abstract into the CommonAbstract.tex file.

We describe new capabilities for modeling bilevel programs within
the Pyomo modeling software.  These capabilities include new modeling
components that represent subproblems, modeling transformations for
re-expressing models with bilevel structure in other forms, and
optimize bilevel programs with meta-solvers that apply transformations
and then perform optimization on the resulting model.  We illustrate
the breadth of Pyomo's modeling capabilities for bilevel programs,
and we describe how Pyomo's meta-solvers can perform local and
global optimization of bilevel programs.

>>>>

We will use this file to document the following:\\
1. Bilevel model forms\\
\indent a. Canonical Model Form (e.g., generic affine or convex constraints, discrete variables?)\\
\indent b. Numerical Example\\
\indent c. Current Pyomo Code for (a)\\
\indent d. How would this be solved?\\
2. Uncertainty model forms\\

\if 0
We describe new capabilities for modeling bilevel programs within
the Pyomo modeling software.  These capabilities include new modeling
components that represent subproblems, modeling transformations for
re-expressing models with bilevel structure in other forms, and
optimize bilevel programs with meta-solvers that apply transformations
and then perform optimization on the resulting model.  We illustrate
the breadth of Pyomo's modeling capabilities for bilevel programs,
and we describe how Pyomo's meta-solvers can perform local and
global optimization of bilevel programs.
\fi
